Assessing the Scientific Value of Amateur Photometric Observations of Binary Star Transits

### 2025-01-04 paper.tex
docs: adding more accurate curves and comparisons
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{imgs/aligned.png}
    \caption{Cleaned data of U Cephei.}
    \label{fig:cleaned_data}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{imgs/light-curve.png}
    \caption{Light curve of U Cephei showing a clear transit event.}
    \label{fig:light_curve}
\end{figure}

The light curve of U Cephei is showing a clear transit event happening, we can see the flux of the star decreasing and then increasing again, as comparaison to the flux of the comparison star.

Only 2 comparision stars are showcased on this graph, but in reality 7 comparision stars were used to get a more accurate result. When looking at their light curve we clearly see that they remain pretty stable throughout the observation,
and normalized around 1, which is a good sign that the data is reliable.

@@

@@

% Discussion
\section{Discussion}
% The findings underscore the feasibility of conducting meaningful photometric observations of binary star systems, such as U Cephei, under suboptimal conditions using personal equipment. While light pollution (Bortle 7) posed challenges, careful calibration and consistent methodology mitigated many of the issues. The results demonstrate the potential for amateur observations to complement professional studies, particularly for systems with frequent or well-documented transits.

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{assets/aligned.png}
    \caption{Cleaned data of U Cephei.}
    \label{fig:cleaned_data}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1\textwidth]{assets/Measurements.png}
    \caption{Light curve of U Cephei showing a clear transit event.}
    \label{fig:light_curve}
\end{figure}

The light curve of U Cephei is showing a clear transit event happening, we can see the flux of the star decreasing and then increasing again, as comparaison to the flux of the comparison star.
I didn't completely trim the data after the transit to showcase the return to normal of the star, we see that from 0.62 to the end the curve seems to stabilize again and become linear.

Only 2 comparision stars are showcased on this graph, but in reality 7 comparision stars were picked to get a more accurate result. When looking at those 2 light curve we clearly see that they remain pretty linear throught the night,
and normalized around 1, which is a good sign that the data is reliable. The pertubations on the light curves can be explained by the fact that the stars are not at the same altitude in the sky, and that the atmosphere can affect the light received by the camera, as well as the fact
this data is collected by an amateur setup.

We also can notive a small gap in the data around the meridian flip since this is not fully automated yet, the telescope had to be flipped manually, which caused a small gap in the data.

@@

To validate the reliability of the amateur observations, I conducted a comparative analysis with professional data from the Transiting Exoplanet Survey Satellite (TESS) mission. The TESS data provided a benchmark for evaluating the precision and accuracy of the amateur observations.

\begin{figure}[h]
    \centering
    \includegraphics[width=1\textwidth]{assets/comparaison.png}
    \caption{Light curve comparaison from TESS data and amateur data.}
    \label{fig:light_curve}
\end{figure}

One thing we see when looking at those light curves is the fact they are not overlapping. This can be explained by the fact that TESS is in space and doesn't have to deal with the atmosphere, making the star looks brighter. It could also be explained by the fact
TESS sensor is more sensitive than the one used in this study, making the star looks brighter. This is why the data is not overlapping, but the transit event is still clearly visible on both light curves.

@@
